---
title: "Additional Statistical Analyses (Revision)"
author:
  name: Takeshi Kondo
  orcid: 0000-0002-3307-671X
editor:
  render-on-save: true
format:
  html:
    code-fold: true
  docx:
    toc: false
---

# Additional Analyses for Peer Review Response

These analyses address specific reviewer and editor comments from the JMIR Medical Education review (Manuscript #90064).

```{r}
#| label: setup
#| message: false
#| warning: false

if (is.null(renv::project())) renv::load()

if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", quietly = TRUE)
pacman::p_load(
  tidyr,
  dplyr,
  ggplot2,
  flextable,
  rio,
  here,
  purrr,
  svglite,
  irr
)

tidy_data <- rio::import(here("data", "quantitative", "data.csv"))
```

## 1. Missing Data Assessment (Editor 9)

```{r}
#| label: tbl-missing-data
#| tbl-cap: "Missing Data Assessment by Variable"

completeness <- tidy_data |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") |>
  mutate(
    n_total = nrow(tidy_data),
    pct_complete = round(100 * (1 - n_missing / n_total), 1)
  )

completeness |>
  rio::export(here("result", "quantitative", "missing_data_assessment.csv"))

completeness |>
  flextable() |>
  set_header_labels(
    variable = "Variable",
    n_missing = "N Missing",
    n_total = "N Total",
    pct_complete = "% Complete"
  ) |>
  align(align = "center", part = "all") |>
  autofit()
```

```{r}
#| label: tbl-record-completeness
#| tbl-cap: "Record-Level Completeness"

record_completeness <- tidy_data |>
  group_by(record_id) |>
  summarise(
    n_rows = n(),
    expected_rows = 20,
    complete = n_rows == 20,
    any_na_value = any(is.na(value)),
    .groups = "drop"
  )

record_summary <- record_completeness |>
  summarise(
    total_records = n(),
    complete_records = sum(complete),
    records_with_na = sum(any_na_value),
    pct_complete = round(100 * mean(complete), 1)
  )

record_completeness |>
  rio::export(here("result", "quantitative", "record_completeness.csv"))

record_summary |>
  flextable() |>
  set_header_labels(
    total_records = "Total Records",
    complete_records = "Complete Records",
    records_with_na = "Records with NA",
    pct_complete = "% Complete"
  ) |>
  align(align = "center", part = "all") |>
  autofit()
```

All `r nrow(tidy_data)` observations across `r length(unique(tidy_data$record_id))` records are complete with no missing values in any variable. Each record contains the expected 20 rows (5 items x 2 persons x 2 assessor types). No imputation procedures or MCAR testing were necessary.

## 2. Student Log Characteristics (Reviewers F5, G1, G2)

### 2.1 Descriptive Statistics

```{r}
#| label: tbl-log-characteristics
#| tbl-cap: "Descriptive Statistics of Student Clinical Log Length (Characters)"

log_data <- tidy_data |>
  distinct(record_id, .keep_all = TRUE)

log_desc <- log_data |>
  summarise(
    n = n(),
    mean = round(mean(log_letter_count), 1),
    sd = round(sd(log_letter_count), 1),
    median = median(log_letter_count),
    q1 = quantile(log_letter_count, 0.25),
    q3 = quantile(log_letter_count, 0.75),
    iqr = IQR(log_letter_count),
    min = min(log_letter_count),
    max = max(log_letter_count)
  )

log_desc |>
  rio::export(here("result", "quantitative", "log_characteristics.csv"))

log_desc |>
  flextable() |>
  set_header_labels(
    n = "N", mean = "Mean", sd = "SD", median = "Median",
    q1 = "Q1", q3 = "Q3", iqr = "IQR", min = "Min", max = "Max"
  ) |>
  align(align = "center", part = "all") |>
  autofit()
```

### 2.2 Distribution

```{r}
#| label: fig-log-length-dist
#| fig-cap: "Distribution of Student Clinical Log Length"

plot_log <- log_data |>
  ggplot(aes(x = log_letter_count)) +
  geom_histogram(bins = 30, fill = "steelblue", alpha = 0.7) +
  labs(x = "Log Length (characters)", y = "Frequency") +
  theme_minimal()

plot_log |>
  ggsave(
    filename = here("result", "quantitative", "fig_log_length_distribution.svg"),
    plot = _, width = 10, height = 6
  )

plot_log
```

### 2.3 Relationship Between Log Length and Score Differences

```{r}
#| label: tbl-log-score-correlation
#| tbl-cap: "Spearman Correlation Between Log Length and Score Difference (AI - Supervisor)"

score_diff_data <- tidy_data |>
  filter(person %in% c("ai", "supervisor")) |>
  select(record_id, assessor_type, item, person, value, log_letter_count) |>
  pivot_wider(names_from = person, values_from = value) |>
  mutate(diff = ai - supervisor)

log_score_corr <- score_diff_data |>
  group_by(item) |>
  summarise(
    n = n(),
    spearman_rho = cor(log_letter_count, diff, method = "spearman", use = "complete.obs"),
    p_value = suppressWarnings(cor.test(log_letter_count, diff, method = "spearman")$p.value),
    .groups = "drop"
  ) |>
  mutate(
    n_tests = n(),
    bonferroni_p = pmin(p_value * n_tests, 1)
  )

log_score_corr |>
  rio::export(here("result", "quantitative", "log_score_difference_correlation.csv"))

log_score_corr |>
  transmute(
    Item = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      TRUE ~ item
    ),
    N = n,
    `Spearman rho` = sprintf("%.3f", spearman_rho),
    `p (uncorrected)` = ifelse(p_value < 0.001, "<.001", sprintf("%.3f", p_value)),
    `p (Bonferroni)` = ifelse(bonferroni_p < 0.001, "<.001", sprintf("%.3f", bonferroni_p))
  ) |>
  flextable() |>
  align(align = "center", part = "all") |>
  autofit()
```

```{r}
#| label: fig-log-score-diff
#| fig-cap: "Relationship Between Log Length and Score Difference (AI - Supervisor)"

plot_scatter <- score_diff_data |>
  mutate(
    item = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      TRUE ~ item
    )
  ) |>
  ggplot(aes(x = log_letter_count, y = diff)) +
  geom_point(alpha = 0.3) +
  geom_smooth(method = "loess", se = TRUE, color = "steelblue") +
  facet_wrap(~ item) +
  labs(x = "Log Length (characters)", y = "Score Difference (AI - Supervisor)") +
  theme_minimal()

plot_scatter |>
  ggsave(
    filename = here("result", "quantitative", "fig_log_length_vs_score_diff.svg"),
    plot = _, width = 12, height = 8
  )

plot_scatter
```

## 3. Normality Testing and Sensitivity Analysis (Reviewer N6)

### 3.1 Shapiro-Wilk Test on Paired Differences

```{r}
#| label: tbl-normality-tests
#| tbl-cap: "Normality Tests and Non-Parametric Sensitivity Analysis"

# Score differences (per item, pooling both assessor types)
paired_scores <- tidy_data |>
  filter(person %in% c("ai", "supervisor")) |>
  mutate(id = paste0(record_id, "_", assessor_type)) |>
  select(id, item, person, value) |>
  pivot_wider(names_from = person, values_from = value) |>
  mutate(diff = ai - supervisor)

normality_scores <- paired_scores |>
  group_by(item) |>
  summarise(
    variable = "Score",
    n = n(),
    shapiro_w = shapiro.test(diff)$statistic,
    shapiro_p = shapiro.test(diff)$p.value,
    wilcox_v = wilcox.test(ai, supervisor, paired = TRUE)$statistic,
    wilcox_p = wilcox.test(ai, supervisor, paired = TRUE)$p.value,
    ttest_p = t.test(ai, supervisor, paired = TRUE)$p.value,
    .groups = "drop"
  )

# Feedback length differences
paired_length <- tidy_data |>
  distinct(record_id, person, .keep_all = TRUE) |>
  filter(person %in% c("ai", "supervisor")) |>
  select(record_id, person, feedback_letter_count) |>
  pivot_wider(names_from = person, values_from = feedback_letter_count)

length_diff <- paired_length$ai - paired_length$supervisor
normality_length <- tibble(
  item = "feedback_length",
  variable = "Length",
  n = length(length_diff),
  shapiro_w = shapiro.test(length_diff)$statistic,
  shapiro_p = shapiro.test(length_diff)$p.value,
  wilcox_v = wilcox.test(paired_length$ai, paired_length$supervisor, paired = TRUE)$statistic,
  wilcox_p = wilcox.test(paired_length$ai, paired_length$supervisor, paired = TRUE)$p.value,
  ttest_p = t.test(paired_length$ai, paired_length$supervisor, paired = TRUE)$p.value
)

normality_all <- bind_rows(normality_scores, normality_length) |>
  mutate(
    n_tests = n(),
    bonferroni_shapiro_p = pmin(shapiro_p * n_tests, 1),
    normal = bonferroni_shapiro_p > 0.05,
    wilcox_sig = wilcox_p < 0.05,
    ttest_sig = ttest_p < 0.05,
    conclusion_same = wilcox_sig == ttest_sig
  )

normality_all |>
  rio::export(here("result", "quantitative", "normality_tests.csv"))

normality_formatted <- normality_all |>
  transmute(
    Variable = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      item == "feedback_length" ~ "Feedback Length",
      TRUE ~ item
    ),
    N = n,
    `Shapiro-Wilk W` = sprintf("%.4f", shapiro_w),
    `Shapiro-Wilk p` = ifelse(shapiro_p < 0.001, "<.001", sprintf("%.3f", shapiro_p)),
    `Wilcoxon V` = sprintf("%.0f", wilcox_v),
    `Wilcoxon p` = ifelse(wilcox_p < 0.001, "<.001", sprintf("%.3f", wilcox_p)),
    `t-test p` = ifelse(ttest_p < 0.001, "<.001", sprintf("%.3f", ttest_p)),
    `Same conclusion` = ifelse(conclusion_same, "Yes", "No")
  )

normality_formatted |>
  rio::export(here("result", "quantitative", "normality_tests_formatted.csv"))

normality_formatted |>
  flextable() |>
  align(align = "center", part = "all") |>
  autofit()
```

### 3.2 Q-Q Plots

```{r}
#| label: fig-qq-plots
#| fig-cap: "Q-Q Plots of Paired Differences (AI - Supervisor) for Each Rubric Item"

qq_data <- paired_scores |>
  mutate(
    item = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      TRUE ~ item
    )
  )

plot_qq <- qq_data |>
  ggplot(aes(sample = diff)) +
  stat_qq() +
  stat_qq_line(color = "red") +
  facet_wrap(~ item, scales = "free") +
  labs(x = "Theoretical Quantiles", y = "Sample Quantiles") +
  theme_minimal()

plot_qq |>
  ggsave(
    filename = here("result", "quantitative", "fig_qq_plots_differences.svg"),
    plot = _, width = 12, height = 8
  )

plot_qq
```

## 4. Effect Sizes (Reviewer G5)

```{r}
#| label: tbl-effect-sizes
#| tbl-cap: "Effect Sizes (Cohen's d) for AI vs Supervisor Comparisons"

# Effect size for feedback length
length_d <- mean(length_diff) / sd(length_diff)
n_length <- length(length_diff)
se_length_d <- sqrt(1 / n_length + length_d^2 / (2 * n_length))

effect_length <- tibble(
  comparison = "Feedback Length",
  n_pairs = n_length,
  mean_diff = mean(length_diff),
  sd_diff = sd(length_diff),
  cohens_d = length_d,
  d_ci_low = length_d - 1.96 * se_length_d,
  d_ci_high = length_d + 1.96 * se_length_d
)

# Effect sizes for rubric items
effect_scores <- paired_scores |>
  group_by(item) |>
  summarise(
    n_pairs = n(),
    mean_diff = mean(diff),
    sd_diff = sd(diff),
    .groups = "drop"
  ) |>
  mutate(
    cohens_d = mean_diff / sd_diff,
    se_d = sqrt(1 / n_pairs + cohens_d^2 / (2 * n_pairs)),
    d_ci_low = cohens_d - 1.96 * se_d,
    d_ci_high = cohens_d + 1.96 * se_d,
    comparison = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      TRUE ~ item
    )
  ) |>
  select(comparison, n_pairs, mean_diff, sd_diff, cohens_d, d_ci_low, d_ci_high)

effect_all <- bind_rows(effect_length, effect_scores) |>
  mutate(
    interpretation = case_when(
      abs(cohens_d) >= 0.8 ~ "Large",
      abs(cohens_d) >= 0.5 ~ "Medium",
      abs(cohens_d) >= 0.2 ~ "Small",
      TRUE ~ "Negligible"
    )
  )

effect_all |>
  rio::export(here("result", "quantitative", "effect_sizes.csv"))

effect_formatted <- effect_all |>
  transmute(
    Comparison = comparison,
    `N pairs` = n_pairs,
    `Mean Diff` = sprintf("%.2f", mean_diff),
    `SD Diff` = sprintf("%.2f", sd_diff),
    `Cohen's d (95% CI)` = sprintf("%.2f (%.2f to %.2f)", cohens_d, d_ci_low, d_ci_high),
    Interpretation = interpretation
  )

effect_formatted |>
  rio::export(here("result", "quantitative", "effect_sizes_formatted.csv"))

effect_formatted |>
  flextable() |>
  align(align = "center", part = "all") |>
  autofit()
```

## 5. Inter-Rater Reliability (Reviewers F8, N5)

Agreement between faculty and student evaluators for the same record.

```{r}
#| label: tbl-irr
#| tbl-cap: "Inter-Rater Reliability Between Faculty and Student Evaluators"

# Prepare data: for each item x person combination, get faculty vs student ratings
irr_data <- tidy_data |>
  select(record_id, assessor_type, item, person, value) |>
  pivot_wider(names_from = assessor_type, values_from = value)

# Compute IRR for each item x person combination
irr_results <- irr_data |>
  group_by(item, person) |>
  group_modify(~ {
    mat <- .x |> select(faculty, student)
    n <- nrow(mat)

    # Percentage agreement
    pct_agree <- mean(mat$faculty == mat$student, na.rm = TRUE) * 100

    # Cohen's weighted kappa (quadratic weights)
    kq <- tryCatch(
      irr::kappa2(mat, weight = "squared"),
      error = function(e) list(value = NA, p.value = NA)
    )

    # ICC (two-way mixed, agreement, single measures)
    icc_res <- tryCatch({
      res <- irr::icc(mat, model = "twoway", type = "agreement", unit = "single")
      list(value = res$value, lbound = res$lbound, ubound = res$ubound, p = res$p.value)
    }, error = function(e) {
      list(value = NA, lbound = NA, ubound = NA, p = NA)
    })

    tibble(
      n = n,
      pct_agreement = pct_agree,
      kappa_quadratic = kq$value,
      kappa_p = kq$p.value,
      icc_value = icc_res$value,
      icc_lower = icc_res$lbound,
      icc_upper = icc_res$ubound,
      icc_p = icc_res$p
    )
  }) |>
  ungroup()

irr_results |>
  rio::export(here("result", "quantitative", "inter_rater_reliability.csv"))

irr_formatted <- irr_results |>
  transmute(
    Item = case_when(
      item == "accurate" ~ "Accurate",
      item == "clear.direction" ~ "Clear Direction",
      item == "criteria.based" ~ "Criteria Based",
      item == "prioritization" ~ "Prioritization",
      item == "supportive" ~ "Supportive",
      TRUE ~ item
    ),
    Person = case_when(
      person == "ai" ~ "AI",
      person == "supervisor" ~ "Supervisor",
      TRUE ~ person
    ),
    N = n,
    `% Agreement` = sprintf("%.1f", pct_agreement),
    `Weighted Kappa` = sprintf("%.3f", kappa_quadratic),
    `Kappa p` = ifelse(kappa_p < 0.001, "<.001", sprintf("%.3f", kappa_p)),
    `ICC (95% CI)` = sprintf("%.3f (%.3f-%.3f)", icc_value, icc_lower, icc_upper),
    `ICC p` = ifelse(icc_p < 0.001, "<.001", sprintf("%.3f", icc_p))
  )

irr_formatted |>
  rio::export(here("result", "quantitative", "inter_rater_reliability_formatted.csv"))

irr_formatted |>
  flextable() |>
  merge_v(j = "Item") |>
  valign(j = "Item", valign = "top") |>
  align(align = "center", part = "all") |>
  autofit()
```

Kappa interpretation (Landis & Koch, 1977): <0 = Poor, 0.00-0.20 = Slight, 0.21-0.40 = Fair, 0.41-0.60 = Moderate, 0.61-0.80 = Substantial, 0.81-1.00 = Almost Perfect.

Note: With ordinal ratings concentrated at 4-5 (ceiling effect), kappa values may appear low even with reasonable agreement. Percentage agreement is reported alongside kappa to provide context.
