---
bibliography: citations.bib
title: "Same logs, different voices: AI-generated vs human feedback during clinical clerkship in undergraduate education"
author:
  - name: Takeshi Kondo
    orcid: 0000-0002-3307-671X
    email: ncukondo@gmail.com
    corresponding: true
    degrees:
      - MD
      - MHPE
      - PhD
    attributes:
      - corresponding: true
    affiliations:
      - ref: nagoya_univ
      - ref: maastricht_univ
  - name: Jeroen Donkers
    orcid: 0000-0002-6769-0355
    email: jeroen.donkers@maastrichtuniversity.nl
    degrees:  
      - PhD
    affiliations:
      - ref: maastricht_univ
      - ref: maastricht_univ_erd
  - name: Hiroshi Nishigori
    degrees:  
      - MD
      - MMEd
      - PhD
    orcid: 0000-0002-0715-7073
    email: hiroshi.nishigori@gmail.com
    affiliations:
      - ref: nagoya_univ
  - name: Sanne Rovers
    orcid: 0000-0002-6391-8121
    email: s.rovers@maastrichtuniversity.nl
    degrees:  
      - PhD
    affiliations:
      - ref: maastricht_univ
      - ref: maastricht_univ_erd
  - name: Sylvia Heeneman
    orcid: 0000-0002-6103-8075
    email: sylvia.heeneman@mumc.nl
    degrees:  
      - PhD
    affiliations:
      - ref: maastricht_univ
      - ref: maastricht_univ_path
affiliations:
  - name: Center for Medical Education, Nagoya University Graduate School of Medicine, Nagoya city, Aichi, Japan
    id: nagoya_univ
    address: 65, Tsurumai-cho, Showa-ku
    city: Nagoya
    state: Aichi
    country: Japan
    postal-code: 466-8550
  - name: The School of Health Professions Education, Maastricht University, Maastricht, The Netherlands
    id: maastricht_univ
  - name: Department of Educational Research and Educational design, Maastricht University, Maastricht, The Netherlands
    id: maastricht_univ_erd
  - name: Department of Pathology, Maastricht University, Maastricht, The Netherlands
    id: maastricht_univ_path
keywords: 
  - artificial intelligence
  - clinical clerkship
  - feedback
  - large language model
  - medical education
  - mixed-methods research
csl: JMIR.csl
figPrefix: Figure
tblPrefix: Table
filters:
  - ./custom-filters/meta-ref.lua
  - ./custom-filters/strip-title-author.lua
editor:
  render-on-save: false
format:
  html: default
  docx:
    reference-doc: reference.docx
  typst: default
---

```{r}
#| echo: false
#| message: false

# setup

if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", quietly = TRUE)
pacman::p_load(
  tidyr,
  dplyr,
  readr,
  here,
  flextable
)

set_flextable_defaults(
  table.layout = "fixed",
  font.size = 9
)
```
## Original Paper

# Same logs, different voices: AI-generated vs human feedback during clinical clerkship in undergraduate education

Takeshi Kondo ,MD, MHPE, PhD; Jeroen Donkers, PhD; Hiroshi Nishigori, MD, MMEd, PhD; Sanne Rovers, PhD; Sylvia Heeneman, PhD

Corresponding author:<br> 
Takeshi Kondo, MD, MHPE, PhD<br>
Department of General Medicine/Family & Community Medicine, Nagoya University Graduate School of Medicine, Nagoya, Japan<br>
65, Tsurumai-cho, Showa-ku,<br>
Nagoya-city, Aichi, <br>
Japan <br>
E-mail: ncukondo@gmail.com; <br>
Tel: +81-52-741-2111<br>
Fax: +81-52-741-2111<br>
ORCID ID: https://orcid.org/0000-0002-3307-671X<br>

## Abstract

**Background:** Feedback is essential for medical students' learning during clinical clerkships, yet supervising physicians often struggle to provide meaningful written feedback due to time constraints. Large language models (LLMs) offer a promising approach to supplement human feedback, but how AI-generated and human feedback differ in authentic clinical settings remains unclear. Previous studies have yielded inconsistent findings regarding feedback length, quality, and distinguishability, with most comparisons conducted in classroom or simulation contexts rather than clinical environments.

**Objective:** To examine how AI-generated feedback and supervisor-provided feedback differ when applied to medical students' clinical clerkship logs, by identifying the distinct characteristics and complementary strengths of each feedback type.

**Methods:** This mixed-methods study employed a convergent design. We collected 161 sets of weekly clinical clerkship logs from fifth- and sixth-year medical students at Nagoya University, Japan, along with corresponding supervisor feedback and AI-generated feedback using GPT-4o. Ten faculty members and ten medical students evaluated both feedback types using a validated rubric assessing five categories: criteria-based, clear directions for improvement, accuracy, prioritization, and supportive tone. Quantitative analyses included paired t-tests, cumulative link mixed models, and correlation analyses. Qualitative thematic analysis examined evaluators' open-ended comments. Results were integrated using Joint Display Analysis.

**Results:** AI feedback was significantly longer than supervisor feedback (mean: 382 vs. 98 characters, p <0.001). AI feedback scored significantly higher on criteria-based (OR=11.81, p<0.001) and clear direction (OR=6.61, p<0.001) categories, with no significant differences in accuracy, prioritization, or supportive tone. AI feedback demonstrated greater quality consistency, while supervisor feedback showed higher variability (variance ratio 3.9:1). For supervisor feedback, length positively correlated with quality scores; no such correlation existed for AI feedback. All evaluators correctly identified feedback sources. Qualitative analysis of open-ended comments revealed five themes: adherence to feedback criteria and structure, continuity and consistency, perspective as a clinician, quality of Japanese language, and text length. AI provided structured, text-anchored feedback following rubric criteria, while supervisors offered experience-based feedback grounded in clinical context and professional expertise that sometimes lacked structured elements.

**Conclusions:** AI-generated and supervisor-provided feedback show distinct but complementary strengths. AI consistently delivers structured, criterion-based feedback aligned with written content, addressing gaps that may arise when time-pressured supervisors provide brief feedback. However, AI lacks the clinical perspective and contextual grounding that supervisors bring from direct observation and professional experience. These findings suggest that AI feedback should complement rather than replace human feedback in clinical clerkship settings, with each type addressing the other's limitations to optimize student learning.


Keywords: {{keywords}}

## Introduction

### Background

Feedback serves as a critical educational instrument for medical students and residents to learn from their experiences in the clinical environment [@Hansen2024-fe;@Ende1983-yv;@Norcini2007-dh;@Burgess2020-tj]. Such feedback can be provided orally or as written feedback [@Elnicki1998-df]. In the clinical environment, where multiple supervising physicians often take turns in providing guidance, obtaining and documenting written feedback is important for ensuring the continuity of learning and assessment [@Harvey2013-hx;@Greviana2024-xd;@van-der-Vleuten2018-hd]. However, supervising physicians in the clinical setting often have multiple tasks, which puts a strain on the time they have to support learning through feedback [@Branfield_Day2020-gi]. Particularly regarding written feedback, supervising physicians are often unable to provide this in a sufficiently elaborated manner [@Branfield_Day2020-gi;@Canavan2010-zh].

To supplement feedback from human supervisors, feedback generation using artificial intelligence (AI) has recently gained attention. In particular, since the advent of large language models (LLMs), the ease of using AI has led to an enthusiastic exploration of its application in feedback [@Lucas2024-rd;@Dai2023-gk;@Jarry-Trujillo2024-kg]. LLMs are AI models that can handle various tasks by pre-training on massive amounts of text data in advance [@Abd-Alrazaq2023-tz]. Although previous AI technologies were also able to generate feedback, they required models trained on context-specific text data tailored to the feedback's domain [@LeCun2015-gf]. In contrast, LLMs can adapt to diverse contexts with minimal modifications, making them promising tools for generation of feedback [@Khan2023-vr;@Lee2023-qp]. When AI feedback and human feedback were compared for feedback generation for texts written by learners, it was shown that AI feedback can match that of well-trained educators in terms of appropriateness, usefulness of the content, and supportive tone [@Steiss2024-ra;@Jarry-Trujillo2024-kg;@Ortega-Ochoa2024-ub]. However, even studies demonstrating that AI can generate high-quality feedback argue that AI feedback should complement rather than replace human feedback, citing student preferences and the responsibility that human instructors should maintain [@Jayawardena2025-gj;@Haider2025-tc;@Cicek2025-ru].

### Rationale and research question

When leveraging AI feedback to complement human feedback, it is important to understand how the two differ. Prior research has reported inconsistent findings regarding these differences. Several studies report that AI feedback is longer and more detailed than human feedback [@Jayawardena2025-gj; @Usher2025-md; @Er2025-is], whereas another study found AI feedback to be shorter and less relevant [@Ali2025-fd]. Although longer feedback is often associated with higher perceived quality [@Andreou2024-mt; @Poeppelman2025-iv; @Lu2023-da], the extent to which differences in length between AI and human feedback translate into quality advantages remains unclear [@Jayawardena2025-gj; @Steiss2024-ra]. For example, in dental histology assignments AI feedback was longer and contained more improvement points than human feedback [@Jayawardena2025-gj], yet an analytical, multi‑criterion comparison showed that human teachers produced feedback that was overall clearer, more accurate, and better prioritized, even when shorter [@Steiss2024-ra]. Regarding the consistency of feedback quality, many studies report that the quality of human feedback varies widely depending on the provider and the situation [@Mooney2022-hy; @Coughlin2022-qj; @Van-Ostaeyen2023-wo], whereas some studies find that, compared with AI, human feedback is consistently higher in quality [@Ali2025-fd;@Lin2024-zt]. Findings are also inconsistent about whether recipients can tell if the feedback provider is AI or human, ranging from studies reporting that people could distinguish it reasonably well [@Nazaretsky2024-sf] to studies reporting that they could hardly distinguish it [@Zhang2025-cg; @Rudian2025-nq]. Thus, although many aspects of AI and human feedback have been examined, the results vary widely. These divergences likely relate to contextual variation such as differences in discipline, task authenticity, assessment purpose.

When comparing AI and humans in other clinical environments including clinical clerkships, a key limitation is that most existing comparisons have examined classroom or simulation tasks rather than authentic clinical activities [@Jayawardena2025-gj; @Usher2025-md; @Er2025-is; @Steiss2024-ra]. In clinical clerkships, supervising physicians work closely with students, allowing feedback to draw on direct observation of behaviors, tacit professional norms, and shared patient care experiences, dimensions that may be difficult to approximate when using AI. Furthermore, prior comparative studies often allowed humans ample preparation time for crafting feedback [@Steiss2024-ra; @Jarry-Trujillo2024-kg; @Ortega-Ochoa2024-ub], whereas in real clinical settings supervisors are time‑pressured and may produce brief or nonspecific comments [@Branfield_Day2020-gi; @Canavan2010-zh]. This specific context constraint could both expose areas where human feedback quality diminishes and highlight domains where AI systems  might compensate given their ability to generate structured output rapidly.

Accordingly, an analytical examination situated within the clinical environment is needed to clarify how AI and human feedback differ when applied to authentic clerkship learning logs under routine time constraints. By exploring these differences, we can identify ways to leverage AI-generated feedback to complement supervisors in the busy clinical environment. Accordingly, our research question is: In what ways and along which dimensions do feedback from supervising physicians and feedback generated by AI differ when applied to medical students’ clinical clerkship logs?

## Methods

### Setting

The research was conducted within the clinical clerkship programs for fifth- and sixth-year medical students at Nagoya University (NU), Japan. In Japan, students enter medical school directly after high school (around age 18) and complete a six-year program [@Nishigori2024-rr]. At NU, medical students finish classroom-based learning in clinical medicine and preparatory training for clinical clerkships (such as medical interviewing and physical examination) by the end of the fourth year. From late fourth to early fifth year they undertake observation-centered clinical clerkships, rotating through all departments for short periods of 1–2 weeks. From late fifth to early sixth year they participate in clinically active clerkships, rotating through each department for four weeks or longer. For this study, we focused on the clinical clerkship program at NU for students in the latter half of their fifth year and throughout their sixth year. The participants were a single cohort of students who began their clinically active clerkships during their fifth year and continued into their sixth year as part of their normal academic progression (the Japanese academic year begins in April). During the clerkship, students join the medical team, examine patients, formulate assessments and plans, and document these in the electronic medical record. Because access to electronic medical records is rigidly restricted, students also record their daily activities, learning points, and future tasks in an e-portfolio system separate from the medical record. These clinical clerkship logs in e-portfolio are used solely for educational purposes, and students are instructed not to include any patient-identifying information. Each daily log entry consists entirely of free-text fields in which students describe what they did during the clerkship, the cases they experienced, what they learned, and what they plan to do next; no Likert scales or structured questions are included, and no upper or lower character limits are imposed. Students entered their logs via smartphone. The e-portfolio automatically compiles the daily entries in the clerkship log into weekly records and sends them to the supervising physicians, who then provide written feedback to the students via the e-portfolio.

### Design

This study was conducted as a mixed-methods study employing a convergent design from a pragmatic perspective [@Fetters2013-ob; @Maudsley2011-wz]. From the pragmatist standpoint of gaining insights that contribute to building a system where AI and supervisors complement each other to promote student learning, we examine the differences between AI-generated feedback and human written feedback on clinical clerkship logs using both quantitative and qualitative approaches. First, we collected feedback from supervising physicians on clinical clerkship logs entered by medical students in the e-portfolio (supervisor feedback) and generated feedback using AI on the clinical clerkship logs (AI feedback), see below for further details of this preparation process. Next, within each dataset the presentation order of the two feedback types (AI vs supervisor) was randomly assigned so that approximately half of the datasets presented AI feedback first and the other half presented supervisor feedback first. This randomization was intended to prevent evaluators from deducing the source of each feedback from its position. The 161 datasets were then randomly distributed among the 10 faculty evaluators and 10 student evaluators; because assignment was random, some evaluators assessed multiple records originating from the same clinical department. Then, medical students and supervising physician evaluators were asked to evaluate both types of feedback. The evaluation used the rubric developed by @Steiss2024-ra for quantitative analysis of scores and qualitative analysis of free-text comments. Finally, the results of the quantitative and qualitative analyses were integrated to gain deeper insights into the differences between AI and supervisor feedback. The process of preparing and evaluating AI feedback and supervisor feedback is shown in [@fig-flow_to_evaluation].

![The process from preparing AI feedback and supervisor feedback to evaluating them](./result/quantitative/Fig_flow_of_feedback_and_evaluation.svg){#fig-flow_to_evaluation}

### Generating AI feedback

On the same set of weekly records of a medical student, feedback was also generated by GPT-4o (gpt-4o-2024-05-13) from OpenAI, which was the latest AI model available from OpenAI as of June 1, 2024, when this feedback was generated. This feedback is called "AI feedback" below.

#### Prompt Development for "AI feedback"

To generate high-quality feedback through LLMs, it is crucial to carefully craft the prompts provided to the LLM [@Jacobsen2023-jl]. Since the students' clinical clerkship logs are written in Japanese and the feedback is for Japanese students, we created the prompts in Japanese. Although @Steiss2024-ra dealt with different types of feedback, their study also compared human-generated descriptions with feedback produced by ChatGPT in response to written tasks. Given the similarities, we decided to adapt the prompts from @Steiss2024-ra as a foundation for our current research. TK, who is a Japanese speaker and familiar with the context where feedback is applied, translated them into Japanese. Additionally, TK referenced papers on prompt creation methods for high-quality feedback generation, adding context and mission elements, as well as criteria for high-quality feedback [@Jacobsen2023-jl]. We then fed these refined prompts and actual student experiential logs into ChatGPT (GPT-4o) web interface to generate feedback. Next, we compared the generated feedback against previously reported quality criteria [@Steiss2024-ra;@Van_Ostaeyen2023-ut] and fine-tuned the prompts accordingly. Finally, to enhance reproducibility and subsequent integration into our e-portfolio system, we employed the corresponding API of the ChatGPT model (OpenAI Chat Completion API (gpt-4o-2024-05-13)) [@OpenAI2024-uk]. Each student log was processed as an independent API call with no shared context between calls, ensuring that feedback for one log could not be influenced by any other log. No maximum token limit (max_tokens parameter) was set at the API level. We will use the term “AI feedback” used in this study below to indicate the feedback that was generated through this API.

The prompt was structured to include sections that established the premise of providing feedback on clinical clerkship logs, explained the structure of these logs, outlined the evaluation criteria for the feedback, and specified the expected content and format of the output. The prompt included an explicit instruction to write the feedback concisely within 500 characters. This character limit was determined through systematic pilot testing in which feedback was generated under various length constraints (no limit, 200, 300, 400, and 600 characters); without any limit, the AI produced verbose output in which key points were diluted, whereas overly restrictive limits resulted in superficial feedback. The 500-character limit was selected as the optimal balance between conciseness and substantive coverage. Supervising physicians received no instructions regarding length, structure, or format for their feedback. For an outline of the prompt construction and revision process, we refer to Multimedia Appendix 1. Since reports were written in Japanese, the prompt was also developed in Japanese. A translation in English of the final prompt is included in the appendix as well as original Japanese version.

### Evaluation of AI and Supervisor Feedback

#### Evaluator Recruitment

Feedback evaluation was conducted by 10 supervising physicians (faculty) and 10 medical students. Because all datasets were divided among the 10 faculty and 10 students, each dataset was evaluated by 1 faculty and 1 student. Eligibility criteria for faculty included their involvement in teaching medical students; for students, those who were either currently participating in clinical clerkships or receiving preparatory education for clinical clerkships were eligible for inclusion in the study. Individuals who authored the student logs used as the basis for the feedback, as well as those who authored the supervisor feedback being evaluated, were excluded from the study. Participants were recruited via a mailing list for medical educators and medical students were recruited through their representatives who disseminated information about the study via social media. They received an explanation about the significance and purpose of the study from the first author (TK) through documentation and an online meeting prior to their participation.

#### Evaluation Instrument

The evaluation instrument consisted of close-ended and open-ended questions. For the close-ended questions we used the scoring rubric developed by Steiss et al @Steiss2024-ra. While there are other criteria used in studies comparing human and AI feedback, most of them employed holistic scoring methods [@Jarry-Trujillo2024-kg; @Ortega-Ochoa2024-ub]. In contrast, Steiss et al @Steiss2024-ra used analytical criteria that evaluate feedback by breaking it down into various elements. This approach aligns with our objective of analyzing how different aspects of feedback differ between humans and AI. This rubric evaluates five categories: criteria-based, clear directions for improvement, accuracy, prioritization of essential features, and supportive tone, each rated with a single score on a 5-point scale. A score of 5 represents the best evaluation, while 1 represents the worst. Each category has descriptive criteria attached. The rubric is presented in Multimedia Appendix 2.

The feedback in this study is in Japanese, and the evaluators are also Japanese, so it was necessary to translate the scoring rubric from English to Japanese. The translation process was conducted based on the TRAPD model [@Walde2023-vi]. This model is designed for the translation of evaluation forms, aiming to perform accurate translations while adapting to linguistic characteristics and cultural contexts that are difficult to address in traditional translation processes, and to maintain the intent of the evaluation forms. This model follows five steps: 1) translation, 2) review, 3) adjudication, 4) pretesting, and 5) documentation. Following these steps, the translation was carried out as described below.

The original feedback quality evaluation rubric [@Steiss2024-ra] was adapted for this study by modifying context-specific terms to fit the current research on student logs. The translation was performed by two bilingual individuals, TK and HN, who are fluent in both Japanese and English and experienced in medical education. The translations were reviewed by a medical education expert (NK). Discrepancies were resolved by a professional translator (OS). Pretesting involved a clinical educator (NY) and a medical student (DI), leading to minor adjustments while preserving the original intent. These detailed processes were documented (see Multimedia Appendix.3). This process ensured the translated questionnaire was culturally and contextually appropriate for use in Japan.

In addition to this rubric, we added a closed question to determine whether the evaluator could identify the source of the feedback, in other words, whether they were accurate in the answer if the feedback was written by a human or generated by AI. This is because previous research has shown that the feedback provider can influence how the feedback is perceived [@van-de-Ridder2014-ld; @Tripodi2021-mc], and understanding how evaluators perceive the feedback provider was considered important for the analysis.

In the open-ended question section of the form, evaluators were asked to freely describe their impressions of the feedback under evaluation, noting its strengths and areas for improvement. Whether the feedback had been generated by AI or written by a supervising physician was not disclosed to them at the time of evaluation, ensuring they based their comments solely on the feedback content.

### Quantitative analysis

All quantitative analyses were conducted in R 4.4.2 [@R-Core-Team2024-jc]. Text length was operationalized as the number of Unicode characters (UTF‑8) in each feedback entry. Since Japanese writing does not use spaces between words, and word counts can vary depending on morphological analysis methods, we used character counts as a more stable metric rather than word counts. Although it varies by domain, Japanese is reported to have approximately 1.7 characters per word [@Zhang2018-kh]. Because each student record had both an AI and a supervisor feedback instance, analyses were paired at the record level and all tests were two‑sided with α = .05; 95% confidence intervals are reported. To examine whether AI and supervisor feedback differed in length, we compared character counts using a paired Student's t‑test across records and visualized the distributions to contextualize any difference in means. To compare perceived quality, we analyzed rubric scores (five ordinal categories: criteria‑based, clear direction, accurate, prioritization, supportive) in two complementary ways. First, for an easily interpretable summary at the record level, we averaged available assessor scores (student and faculty) within provider and item and then used paired t‑tests to compare AI and supervisor mean scores across records. Second, acknowledging the ordinal nature of the outcomes, we fitted cumulative link mixed model. For each item, the fixed effects were feedback provider (AI vs supervisor) and assessor type (student vs faculty), with their interaction examined exploratorily, and a random intercept for assessor to account for clustering. Results are presented as odds ratios with 95% confidence intervals and p‑values under the proportional‑odds assumption. To assess consistency in feedback quality, we computed the per‑record mean score for each provider and compared dispersion between AI and supervisors. Variance differences were tested using Levene's test for equality of variances and corroborated with the classical F‑test, alongside distributional plots of the per‑record means. To evaluate whether longer feedback tended to receive higher scores, we estimated Spearman's rank correlations between character count and rubric scores separately by provider and item, reporting correlation coefficients and two‑sided p‑values. Finally, for the identification task, we summarized detection accuracy as the proportion of correctly identified sources (AI vs supervisor). Bonferroni correction was applied to correct for multiple testing.

#### Sample size calculation

The required sample size for the t-test was calculated using the values published in the paper by @Steiss2024-ra, that developed the rubric used for quantitative analysis. The paper reported effect sizes in terms of Partial eta-squared and Cohen's d, which were used to calculate the sample size. In this study, considering the comparison between AI and supervisor feedback, the sample size was calculated based on Cohen's d of 0.34 as reported by Steiss et al [@Steiss2024-ra]. With power set at 0.8 and alpha at 0.05, 155 data points per group would be needed.

### Qualitative analysis

For the qualitative analysis, narrative comments from the open questions were organized in a table, followed by a thematic analysis [@Nowell2017-qr]. Thematic analysis consists of the following steps: (1) Familiarize with the data, (2) Generate initial codes, (3) Search for themes, (4) Review themes, (5) Define and name themes, and (6) Produce the report [@Nowell2017-qr]. Steps 1 and 2 were conducted by two individuals, TK and HN. TK created the initial codes, while HN reviewed and refined them. They then discussed until reaching agreement. Steps 1 and 2 were conducted in Japanese, while steps 3 to 6 were conducted in English. From step 3 onwards, the codes were translated into English, and SH, SR, and JD also participated. This allowed for a more multifaceted analysis. The backgrounds of TK, HN, SH, SR, and JD are described below.

#### Reflexivity

TK is a general practitioner directly involved in clinical clerkships and also engaged in the development of e-portfolios and feedback. HN is an expert in medical education, researching professionalism in medical education. SH researches e-portfolios and programmatic assessment in health professions education, SR is an expert in self-regulated learning and assessment, and JD is a specialist in statistics and AI.

TK's knowledge about the context of clinical clerkship feedback provision helps in making contextually informed deeper analysis when interpreting descriptions, while TK's involvement in the development of e-portfolios might lead to potential bias where results could be interpreted more favorably toward e-portfolios. The specialized fields of HN, SH, SR, and JD each provide expert perspectives when analyzing descriptions. On the other hand, there is a possibility of biased interpretations based on their respective specialties. To mitigate such biases, discussions were recorded and transparency was maintained during the analysis process, with regular meetings to share and discuss their respective interpretations.

### Integration of results

The results of the quantitative and qualitative analyses were documented separately and then integrated using Joint Display Analysis (JDA). JDA is an analytic strategy in mixed-methods research that brings qualitative and quantitative evidence together in a single, structured visual (a “joint display”) to enable explicit integration and the drawing of meta-inferences that would be difficult to see from either strand alone [@Guetterman2015-qt; @McCrudden2021-eo]. In this study, the results of the quantitative and qualitative analyses were compared and integrated using JDA. Specifically, the quantitative results were tabulated, and the themes identified in the qualitative analysis were listed alongside them. The relationships between the quantitative results and qualitative themes were then examined, and meta-inferences were drawn.

### Ethical considerations

This study was approved by the Ethics Committee of Nagoya University Hospital (approval number: 2023-0451). An opt-out approach was taken for the research use of student clinical clerkship logs and supervisor feedback accumulated in the e-portfolio. Before the clerkship, all medical students received an explanation from TK via online meetings regarding the use of clinical clerkship logs in e-portfolio for research purposes and were informed that they could opt out by sending an email to a designated address. Supervising participants received explanations from TK via email and, upon request, online meetings regarding the use of feedback recorded in the e-portfolio and were likewise informed that they could opt out by sending an email to a designated address. Research participants who evaluated AI feedback and supervisor feedback were recruited using an opt-in approach. All evaluators provided informed consent before participating. Student clinical clerkship logs, supervisor feedback, AI feedback, and evaluator assessment data used in the research were anonymized for analysis. All proper nouns were replaced with alphabetic characters, and linking tables were managed in an encrypted state.

## Results

During the clinical clerkship conducted at Nagoya University from January 9, 2024, to May 5, 2024, combinations of student clerkship logs and corresponding supervisor feedback were collected. The data included nine clinical departments and three community hospitals, involving a total of 47 medical students and 42 supervisors who contributed to the clerkship logs and feedback. On June 1, 2024, AI feedback was generated for the student clerkship logs. As a result, a total of 161 datasets were created, each consisting of a student's clerkship logs for one week, supervisor feedback, and AI feedback. The weekly clerkship logs varied considerably in length (mean 675.2 characters, SD 459.8; median 551; range 51–2,342). The number of datasets, students, and supervisors by department is shown in [@tbl-dataset_summary].


```{r}
#| echo: false
#| message: false
#| label: tbl-dataset_summary
#| tbl-cap: Dataset Summary
#| tbl-footnote: "Except for A, B, and C Community Hospital, all departments are affiliated with Nagoya University. ^2 The total number of students exceeds 47 because some students rotated through multiple departments."

df <- read.csv(here("result", "quantitative", "dataset_summary.csv"))

avail <- 6
w <- rep(avail /ncol(df), ncol(df))

df |>
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = w) |>
  set_header_labels(
    department = "Department*",
    dataset_count = "Number of datasets",
    students = "Number of students†",
    supervisors = "Number of supervisors‡"
  ) |>
  theme_vanilla() |>
  add_footer_lines(c("*Except for A, B, and C Community Hospital, all departments are affiliated with Nagoya University.", "†The total number of students exceeds 47 because some students rotated through multiple departments.","‡The total number of supervisors exceeds 42 because some supervisors provided feedback in multiple departments.")) |>
  fontsize(part = "footer", size = 9) |>
  italic(part = "footer")


```


From October 2024 to January 2025, 10 medical students and 10 faculty who were not involved in the creation of the above student clerkship logs or feedback evaluated the AI and supervisor feedback. No missing data were identified; all 161 records contained complete rubric scores from both assessors across all five items, yielding 3,220 observations with 100% data completeness.

### Quantitative analysis

#### Distribution Assessment and Sensitivity Analysis

Shapiro-Wilk tests assessed the normality of paired differences for all comparisons. The feedback length difference was normally distributed (W = 0.992, p = .550), supporting the use of the paired t-test for that variable. However, all five rubric score differences departed significantly from normality (all W ≤ 0.939, all p < .001 after Bonferroni correction). As a sensitivity analysis, Wilcoxon signed-rank tests were conducted alongside the paired t-tests; the two methods yielded identical conclusions regarding statistical significance for every variable. Moreover, the primary analysis of rubric scores employed cumulative link mixed models (see below), which do not assume normality of the outcome distribution.

#### Difference Between Feedback Length

The length of the feedback was compared between AI and supervisor feedback. Mean lengths were 382.02(95% CI 369.29-394.76) characters for AI and 97.87(95% CI 86.4-109.33) characters for supervisors. The distribution of the lengths of supervisor feedback and AI feedback is shown in [@fig-length_distribution]. Paired t-test results indicated that the mean character count of AI feedback was significantly higher than that of supervisor feedback (mean difference 284.16 characters; 95% CI 268.6-299.71; p <0.001; Cohen's d = 2.84, 95% CI 2.50–3.19).

![Distribution of feedback lengths by character count](result/quantitative/fig_length_distribution.svg){#fig-length_distribution}

#### Comparison of Scores

The scores assigned by the evaluators to the AI and supervisor feedback were compared. @fig-diff-ai-vs-supervisor shows the differences in feedback scores by AI and supervisors for the same log. Values greater than 0 indicate that the AI score is higher, and values less than 0 indicate that the supervisor score is higher. Although there are slight differences among evaluators, AI scores tend to be higher except for the “supportive” item.

![Distribution of Scores for Each Category ](result/quantitative/fig_diff_ai_vs_supervisor.svg){#fig-diff-ai-vs-supervisor}

Next, we compared the mean scores of AI and supervisor feedback for each category. In all categories, AI feedback had higher mean scores than supervisor feedback. A t-test comparing the mean scores of supervisor feedback and AI feedback showed that AI feedback was rated significantly higher in all categories after Bonferroni correction: criteria-based (corrected p < 0.001), clear direction (corrected p < 0.001), prioritization (corrected p < 0.001), accurate (corrected p < 0.001), and supportive (corrected p = 0.011). Details including uncorrected p-values are shown in [@tbl-paired_ttest_results].

```{r}
#| label: tbl-paired_ttest_results
#| tbl-cap: Paired T-test Results Comparing AI and Supervisor Feedback Scores
#| echo: false

df <- read.csv(here("result", "quantitative", "paired_ttest_results_formatted.csv"))

avail <- 6
w <- rep(avail /ncol(df), ncol(df))

df |> 
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = w) |>
  set_header_labels(
    Item = "Item",
    mean_ai = "AI Mean Score (95% CI)",
    mean_supervisor = "Supervisor Mean Score (95% CI)",
    mean_diff = "Mean Difference (95% CI)",
    cohens_d = "Cohen's d (95% CI)",
    p_uncorrected = "p-value",
    p_bonferroni = "Corrected p-value"
  ) |>
  fontsize(size = 8, part = "all") |>
  theme_vanilla()

```

Because the rubric used for scoring is a 5-point scale and the intervals from 1 to 5 may not be equal, using average scores may not be appropriate. Therefore, we used ordinal logistic regression to examine whether there are differences between AI and supervisors scores. We also employed a mixed-effects ordinal model to account for assessor type (student or faculty) and random effects by assessor. The results are shown in @tbl-ordinal-regression-clmm. In the ordinal logistic regression, three effects are expressed as odds ratios (OR) for each category. "Provider: AI" indicates that the larger the OR above 1, the more likely AI is to receive higher scores compared to supervisors. "Assessor type: student" indicates that the larger the OR above 1, the more likely students are to give higher scores compared to faculty. "Interaction: supervisor × student" indicates that the larger the OR above 1, the greater the difference in scores between AI and supervisors among students compared to faculty. P-values are Bonferroni-corrected for comparisons across 15 items. The results indicated that, for the items criteria based, and clear direction, AI feedback received significantly higher scores than supervisor feedback (OR = 11.81 [95% CI: 7.64–18.27], p < 0.001; OR = 6.61 [95% CI: 4.35–10.06], p < 0.001) (OR, odds-ratio, values larger than 1 indicate higher scores for AI than for supervisors). For accurate, prioritization, and supportive, AI also tended to receive higher scores, but the differences between AI and supervisors were not significant (OR = 1.35 [95% CI: 0.91–2.00], p = 1.000; OR = 1.70 [95% CI: 1.16–2.50], p = 0.098; OR = 1.34 [95% CI: 0.87–2.06], p = 1.000). Regarding assessor type (student vs faculty), no significant differences were observed in any of the items. We also included interaction terms to test whether the effects of AI vs supervisor depended on assessor type, but no significant interaction effects were observed for any item.

```{r}
#| label: tbl-ordinal-regression-clmm
#| tbl-cap: Cumulative Link Mixed Models Results Comparing AI and Supervisor Feedback Scores
#| echo: false

df <- read.csv(here("result", "quantitative", "clmm_summary_formatted_bonferroni.csv"))
df |>
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = c(1, 2.2, 1.4, 0.7, 0.7)) |>
  flextable::merge_v(j = "Item") |>
  set_header_labels(
    Item = "Item",
    Effect = "Effect",
    OR = "OR (95% CI)",
    p_uncorrected = "p-value",
    p_bonferroni = "Corrected p-value"
  ) |>
  fontsize(size = 8, part = "all") |>
  theme_vanilla()
```


#### Consistency of Feedback Quality

To compare the consistency of feedback quality between AI and supervisors, we plotted the distribution of per-clinical clerkship log mean scores (see @fig-mean-score-per-record). AI exhibited smaller score dispersion, suggesting higher consistency in feedback quality. We further tested whether the variance of per-clinical clerkship log mean scores differs between AI and supervisors. The variance of per-clinical clerkship log mean scores was significantly larger for supervisors (Var=1.011, SD=1.005) than for AI (Var=0.262, SD=0.512) (Levene: F(1, 320)=73.203, p<.001; F-test: F(160, 160)=0.259, p<.001). The supervisor variance was about 3.9 times that of AI, suggesting that AI feedback quality is more consistent, whereas supervisor feedback quality is more variable.

![Distribution of Mean Scores per Record](result/quantitative/fig_mean_score_per_record.svg){#fig-mean-score-per-record}

#### Correlation between feedback length and score

To investigate whether the character count of feedback is correlated with the scores given by evaluators, we calculated the Spearman's rank correlation coefficient for each feedback provider. The results are summarized in @tbl-correlation-between-letter-count-and-score. p-values are Bonferroni-corrected for comparisons across 10 items. A significant positive correlation would suggest that longer feedback tends to receive higher scores. No significant correlation was observed between text length and score for AI, but a significant correlation was found for all item categories for supervisors. This suggests that longer feedback from supervisors tends to receive higher scores.

```{r}
#| label: tbl-correlation-between-letter-count-and-score
#| tbl-cap: "Correlation between Letter Count and Score for Each Feedback Provider"
#| echo: false

df <- read.csv(here("result", "quantitative", "correlation_letter_count_score_by_person_item_formatted.csv"))

# Reshape the data to have separate columns for each feedback provider
df_wide <- df |>
  pivot_wider(
    names_from = feedback_provider,
    values_from = c(spearman, p_value),
    names_sep = "_"
  ) |>
  select(
    Item,
    spearman_AI,
    spearman_Supervisor,
    p_value_AI,
    p_value_Supervisor
  )

avail <- 6
w <- rep(avail / ncol(df_wide), ncol(df_wide))

df_wide |> 
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = w) |>
  set_header_labels(
    Item = "Item",
    spearman_AI = "AI",
    spearman_Supervisor = "Supervisor", 
    p_value_AI = "AI",
    p_value_Supervisor = "Supervisor"
  ) |>
  add_header_row(values = c("", "Spearman's ρ", "Corrected p-value"), colwidths = c(1,2,2)) |>
  theme_vanilla() |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(align = "left", part = "body", j = 1) |>
    flextable::align(align = "center", part = "body", j = 2:ncol(df_wide))

```

#### Relationship Between Student Log Length and Feedback Scores

Because AI feedback is tightly text-anchored, variation in student log quality could potentially influence feedback scores. To examine whether log length influenced rubric scores, Spearman correlations were calculated between weekly log character count and each rubric score, separately by feedback provider. After Bonferroni correction for 10 comparisons, no significant correlations were observed for either AI or supervisor feedback (all corrected p > .05), indicating that variation in student log length did not systematically influence rubric scores for either feedback type.

#### Inter-Rater Reliability

Because each dataset was independently evaluated by one faculty member and one student, we examined agreement between these two assessor types using weighted Cohen's kappa (quadratic weights) and intraclass correlation coefficients (ICC), computed separately for AI and supervisor feedback across all five rubric items (@tbl-inter-rater-reliability). For supervisor feedback, inter-rater agreement was fair to moderate (weighted κ = 0.37–0.54, all p < .001). For AI feedback, agreement was poor (weighted κ = 0.04–0.15, mostly non-significant). This pattern suggests that faculty and student evaluators reached more consistent judgments when rating supervisor feedback than when rating AI feedback.

```{r}
#| label: tbl-inter-rater-reliability
#| tbl-cap: Inter-Rater Reliability Between Faculty and Student Evaluators
#| echo: false

df <- read.csv(here("result", "quantitative", "inter_rater_reliability_formatted.csv"))

avail <- 6
w <- rep(avail / ncol(df), ncol(df))

df |>
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = w) |>
  set_header_labels(
    Item = "Item",
    Person = "Feedback Type",
    N = "N",
    X..Agreement = "% Agreement",
    Weighted.Kappa = "Weighted κ",
    Kappa.p = "κ p-value",
    ICC..95..CI. = "ICC (95% CI)",
    ICC.p = "ICC p-value"
  ) |>
  fontsize(size = 8, part = "all") |>
  theme_vanilla()
```

#### Identification of Feedback Source

The evaluators were asked whether they could identify the source of the feedback, specifically whether it was generated by a human or an AI. All students and supervisors correctly identified the source for every item (100% detection accuracy).

### Qualitative analysis

The qualitative analysis of the free-text comments provided by the evaluators revealed several themes regarding the differences between AI and supervisor feedback. The themes are shown in @tbl-themes.

```{r}
#| label: tbl-themes
#| tbl-cap: Categorized Themes Identified in Qualitative Analysis
#| echo: false

df <- read.csv(here("result", "qualitative", "theme_table_en_simple.csv")) |>
  pivot_wider(
    names_from = provider,
    values_from = sub_theme,
    values_fn = function(x) paste0("- ", x, collapse = "\n")
  )
avail <- 6
w <- rep(avail /ncol(df), ncol(df))
df |> 
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = w) |>
  flextable::merge_v(j = "theme") |>
  set_header_labels(
    theme = "Theme",
    AI = "Sub themes for AI",
    supervisor = "Sub themes for Supervisor"
  ) |>
  theme_vanilla()
```

Five themes were identified as differences between AI and supervisor feedback: "Adherence to the feedback criteria and structure", "Continuity and consistency", "Perspective as a clinician", "Quality of the Japanese language", and "Text length". Below we describe the details of these themes. Citations consist of IDs with three parts. When the first part is "AI_", it indicates comments about AI feedback, and when it is "SU_", it indicates comments about supervisor feedback. The second part shows "_FA" for comments by faculty evaluators and "_ST" for comments by student evaluators. The number in the latter half represents the evaluator ID. The final part indicates the dataset ID.

#### Adherence to the feedback criteria and structure

Across comments, AI‑generated feedback was repeatedly described as tightly aligned with the rubric and highly structured. Evaluators highlighted concrete, example‑driven suggestions, clear prioritization, and a predictable structure. This structure made next steps “easy to put into practice,” but some judged it overly prescriptive or formulaic. By contrast, supervisor feedback often departed from the rubric’s structure: at times it omitted actionable “points for improvement,” offered too few details, or listed many items without prioritization. Several comments, however, framed these departures as deliberate, “living” feedback rooted in real clinical work rather than in formal criteria.

Illustrative comments included: “This is a well-written report that starts with positive feedback, is specific and constructive, and doesn't have too many points” (AI_FA07_060); “It goes from positive to constructive… priorities are also pointed out… good feedback” (AI_FA07_063); and “It is very specific and detailed. It is written in the classic P‑N‑P format.…” (AI_FA09_086). On limits of the AI style, evaluators noted it could feel templated or prescriptive, e.g., “sentences were… not natural” (AI_ST18_078) and “it would be better if the suggestions for revision were not given in specific sentences” (AI_ST20_115). For supervisors, one comment praised specificity but worried that “there are many items, there is no priority, and it seems a little harsh” (SU_FA07_058), while many others pointed out missing action points: “There is no specific feedback…” (SU_FA13_163) and “No evaluation was given at all. No feedback… on areas for improvement” (SU_ST21_131). Several remarks captured the trade‑off: “In terms of referring to the evaluation criteria, it is inferior… but it is more in line with the content of the practical training and presents the next task” (SU_FA11_127), and “It's not feedback that is tailored to a standard, but it feels like ‘living’ feedback that is likely to bring about behavioral change” (SU_FA09_088).

#### Continuity and consistency

Across evaluators, continuity and consistency emerged as a defining difference in how AI and supervising physicians oriented their feedback. AI feedback typically exhibited strong internal coherence with the student's clerkship log. It read closely, mirrored the structure of entries, and translated what was on the page into concrete, criterion‑referenced suggestions. This text‑anchored continuity helped AI surface specific, actionable edits to the log itself. At the same time, because AI focused only on the student clerkship log, it could miss or misinterpret the broader practicum context, weekend schedules, orientation days, unit norms, or feasibility in busy wards, and offered fewer comments about attitudes, behaviors, or clinical reasoning unfolding across the rotation. In contrast, supervising physicians showed continuity with the clinical experience. Their feedback often drew on shared encounters, observed behaviors, and ward‑based realities, which gave comments a sense of lived coherence over time. However, that experiential continuity did not reliably connect back to the student's written descriptions. Many supervisor comments were brief, global, or focused on the clinical day rather than the clerkship log, creating a misalignment.

This pattern was visible in how AI consistently tied remarks to what students had written, “the feedback is tailored to the  clinical clerkship logs… points that need to be improved… are mentioned in detail, with specific examples” (AI_ST15_031), and “careful guidance in response to the lack of clinical clerkship logs… specific suggestions for improvement” (AI_ST15_030). Evaluators repeatedly noted that AI “gave feedback after the log had been carefully examined… [with] very specific” next steps (AI_ST21_117) and that its “comments are based on the content” (AI_FA05_034). Yet this text‑level consistency sometimes slipped when context mattered: AI “gives the impression that days without logs = days without practice” (AI_FA10_104), and tended to “encourage learning by improving how they write… [with] a lack of clinical knowledge or perspective” (AI_ST21_121). Several evaluators wished for an overarching synthesis across the week or rotation, “no overall evaluation… perhaps (AI was) a good micro‑manager?” (AI_FA11_117), and “it would be even better if the feedback also took into account the overall outcome” (AI_FA10_109). By contrast, supervisors frequently referenced shared clinical situations and behaviors, “useful because it gave supplementary information that wasn't included in the medical student's description” (SU_ST17_062); advice that was “practical and in line with real clinical practice” (SU_ST18_080); and impressions that only a clinician observing the student could offer, such as “he was going about things in a calm and collected way” (SU_ST23_157) and the feeling of “working together with medical students” (SU_FA04_008). However, this experiential continuity often bypassed the portfolio itself: “no mention of the content of the practical training or the learner's own description” (SU_FA10_109); “they did not evaluate the logs that was written… just a summary evaluation conclusion” (SU_FA11_119); and “feedback was based on the actual content of the practical training… it would be better if there was more feedback on the learning logs” (SU_ST21_124). In some instances, identical or near‑identical messages suggested time‑pressured reuse rather than log‑specific engagement (e.g., “copied and pasted feedback,” SU_ST23_164). Taken together, the data indicate that AI maintained continuity with what students wrote, whereas supervisors maintained continuity with what students did, each affording a different, and at times incomplete, alignment with the students' log.

#### Perspective as a clinician

Evaluators frequently contrasted the clinical lens. AI feedback was perceived as strong on structure yet often thin on clinical reasoning, occasionally overlooking medical inaccuracies or proposing improvements not grounded in specialty‑specific practice. Supervisor feedback, in turn, more often drew on clinical judgment, flagging errors, supplying pathophysiologic rationale, and pointing learners toward consequential problems, though some comments cautioned that supervisors can import their own priorities (e.g., recruitment messages, niche emphases) or inadvertently signal an authority gradient.

Comments underscoring AI’s limits included: “did not point out the errors in the words ‘pulse irregularity’ and ‘electrocardiogram holder’” (AI_FA11_120); “specific examples… are ideas that are not based on much medical expertise” (AI_ST22_143); “suggestions for improvement… are not from the surgeon's perspective” (AI_FA06_050); “fixated on relatively trivial points… specific feedback lacks accurate knowledge” (AI_ST15_024); and “main points were comments on how to fill in the student logs… lack of clinical feedback” (AI_ST21_123). By contrast, supervisor excerpts highlighted the expert stance: “points out errors in writing and correctly teaches medical knowledge” (SU_FA06_037); “I can get feedback on my knowledge, so it is useful for my studies” (SU_ST17_058); and advice “that would only be conveyed by a clinician, such as the long‑term perspective of ‘going home’” (SU_ST23_150). Potential downsides were also noted: “content is more focused on recruiting students to the department” (SU_FA05_022) and concerns about prioritization, “few opportunities to do peripheral nerve examinations, but… whether this is something that all medical students should learn” (SU_FA10_110). as well as an authority gradient as exemplified by the following quote:“show the superiority and infallibility of the instructor...makes learners feel an authority gradient” (SU_FA10_108).


#### Quality of the Japanese language

Language quality emerged as a salient differentiator. AI feedback was often experienced as translation‑like, occasionally inconsistent, and at times marred by formatting artifacts. Such phrasing could undermine credibility or supportive tone even when the substantive guidance was sound. Supervisor language, by comparison, was more often described as natural, human, and relationship‑affirming.

Illustrative appraisals of AI language included: “Expressions such as ‘Great job!’ and ‘I will provide feedback.’ are English‑Japanese translation‑like… unnatural as Japanese” (AI_ST23_149); “mysterious extra characters” (AI_ST18_083); “divided into paragraphs… a bug or character corruption” (AI_FA08_083); and “very ChatGPT‑like” (AI_ST17_054). Several noted formulaic tone: “the sandwich of good points… is so formulaic that… students might stop reading the feedback seriously” (AI_ST14_014), alongside word choice that “gives the impression of being a little unfriendly” (AI_FA10_108). In contrast, supervisor comments emphasized naturalness and human presence: “the advice is very good, accurate and natural” (SU_ST18_079) and “it feels like the individual is being looked at and taught” (SU_ST20_109).

#### Text length

Across the dataset, AI feedback tended to be substantially longer, often enumerating many points and including concrete examples. Participants suggested this length may help make expectations explicit and actionable, yet also noted that verbosity can hinder readability and reduce salience of key priorities. By contrast, supervisor feedback was frequently very short—sometimes so brief that essential elements (e.g., specific points for improvement) were missing. Still, several comments valued concision when it clearly conveyed the main point and respected time constraints.

Exemplars included the AI being “somewhat verbose” (AI_ST23_155) with “so many points… it would be easier to understand if there was a summary” (AI_ST16_047). For supervisors, multiple comments judged entries too brief: “not possible to give feedback with just a few words” (SU_ST16_044); “just too short” (SU_FA05_020); “I don't think a simple ‘Thank you for your hard work’ would be considered feedback” (SU_FA09_094); and “too simple and doesn't amount to feedback” (SU_FA11_131). A counterexample highlighted that brevity can still work when targeted: “concise feedback that includes the necessary content… motivates the student for future practice” (SU_ST15_034).

### Integration of Quantitative and Qualitative Results

JDA was used to integrate the results of the quantitative and qualitative analyses. The integration of quantitative and qualitative findings reveals six convergent patterns that illuminate the differences between AI-generated and supervisor-provided feedback. The results of the quantitative analysis are shown in the second column of @tbl-joint_display, while the themes identified in the qualitative analysis are shown in the third column. The fourth column shows how the quantitative and qualitative results are related. Below, we explain the integrated insights obtained from each row.

```{r}
#| label: tbl-joint_display
#| tbl-cap: Joint Display Integrating Quantitative and Qualitative Results
#| echo: false

df <- read.csv(here("result", "integration", "joint_display_analysis.csv")) |>
  mutate(Index = row_number(), .before = 1)

avail <- 6
w <- rep(avail /ncol(df), ncol(df))
df |> 
  flextable() |>
  flextable::set_table_properties(layout = "fixed") |>
  flextable::width(width = c(0.6,1.8,1.8,1.8)) |>
  set_header_labels(
    Quantitative.Analysis = "Quantitative Results",
    Qualitative.Analysis = "Qualitative Results",
    Type.of.Integration = "Type of Integration"
  ) |>
  theme_vanilla()
```


#### Index 1: Text Length and Feedback Quality

The quantitative finding that AI feedback was significantly longer than supervisor feedback was substantiated by the qualitative theme of text length. Qualitative analysis revealed that AI feedback length enabled provision of specific examples, contributing to clarity, while potentially resulting in verbose expressions with unclear priorities. Conversely, supervisor feedback brevity sometimes led to missing important elements but could be highly effective when concise and targeted. This integration demonstrates that qualitative findings explain the impact of length differences on feedback quality, which quantitative analysis alone could not reveal.

#### Index 2: Adherence to Rubric Criteria

The quantitative results showing AI feedback scored significantly higher in clear direction and criteria-based categories, with higher trends in other rubric items, were complemented by qualitative findings regarding adherence to feedback criteria and structure, as well as text length. Qualitative analysis revealed that AI feedback followed the rubric with clear structure and provided actionable points, whereas supervisor feedback was often too brief and lacking some required elements. The significant difference in feedback length was also demonstrated quantitatively. This complementary integration explains how AI feedback meets the elements required by the rubric through both structural adherence and sufficient length.

#### Index 3: Length-Quality Correlation Patterns

A particularly illuminating pattern emerged from combining quantitative correlation analysis with qualitative text length observations. Quantitative examination revealed that while there was no correlation between length and quality in AI feedback, longer submissions received higher scores in supervisor feedback. Qualitative examination showed that AI feedback length enables specific examples to be provided, leading to clarity, while potentially resulting in verbose expressions with unclear priorities. Supervisor feedback brevity can lead to missing important elements but can be highly effective when concise and targeted. This suggests that AI excels at covering necessary elements, while supervisors excel at contextual prioritization. Combining these findings reveals that feedback requires sufficient length to include necessary items, while prioritization is also important, and longer is not necessarily better.

#### Index 4: Quality Consistency and Variability

The quantitative finding that AI feedback quality was more consistent while supervisor feedback quality was more variable was supported by qualitative observations regarding adherence to feedback criteria and structure. The qualitative analysis described AI feedback as closely following the rubric, leading to more uniform quality, whereas supervisors often deviated from the rubric, resulting in variable quality. This integration demonstrates how structural consistency in AI feedback translates directly into measurable quality consistency.

#### Index 5: Clinical Context and Perspective

The quantitative results regarding rubric scores were expanded by qualitative themes of continuity and consistency, as well as perspective as a clinician. Qualitative analysis revealed that AI feedback maintained continuity with written logs and provided specific text-level suggestions while missing broader clinical context. In contrast, supervisor feedback aligned with clinical experience but often failed to engage with specific portfolio content. These qualitative findings revealed aspects beyond those evaluated by the rubric, specifically demonstrating that supervisor feedback was grounded in clinical context and utilized expert perspectives, showing advantages not captured by the rubric scores.

#### Index 6: Distinguishability of Feedback Sources

The quantitative finding that all evaluators could completely distinguish between AI and supervisor feedback was explained by all five qualitative themes identified in the analysis. The themes of adherence to feedback criteria and structure, continuity and consistency, perspective as a clinician, quality of Japanese language, and text length each highlighted distinct differences between the two feedback sources. AI feedback followed the rubric with clear structure, maintained continuity with written logs, and was long with specific examples, while supervisor feedback excelled at contextual prioritization and provided feedback from a clinician perspective with natural, human expressions. These differences suggest why evaluators could distinguish feedback providers, though the analysis cannot determine whether evaluators considered these factors in combination or whether specific elements were decisive in their identification process.

## Discussion

### Principal Findings

This study compared AI-generated feedback with supervisor-provided feedback on medical student clinical clerkship logs through mixed-methods analysis,integrating results using a Joint Display Analysis. AI feedback was significantly longer and demonstrated superior adherence to rubric-based criteria, particularly in providing criteria-based guidance and clear directions for improvement. While supervisor feedback showed greater variability in quality, with length correlating positively with perceived quality, AI feedback maintained consistent quality regardless of length, suggesting systematic coverage of necessary elements. Qualitative analysis revealed complementary strengths: AI provided text-anchored feedback with structured, comprehensive coverage of student log content, while supervisors offered experience-based insights grounded in clinical context and professional expertise. Despite AI's structural advantages, supervisor feedback was valued for its clinical perspective and natural language use. All evaluators could reliably distinguish between the two feedback sources, reflecting substantial differences in approach, structure, and content focus.

### Comparison with the Literature

Our findings align with and extend previous research on AI-generated feedback in several key areas. Regarding feedback length, prior studies have reported various findings [@Jayawardena2025-gj; @Usher2025-md; @Er2025-is; @Ali2025-fd]. Our study demonstrated that AI feedback was significantly longer than supervisor feedback, which is consistent with some previous findings [@Jayawardena2025-gj; @Usher2025-md; @Er2025-is]. In our research, the supervisors providing feedback were working in busy clinical environments, which likely contributed to their tendency to provide shorter feedback. Furthermore, our results showed no correlation between AI feedback length and quality, while supervisor feedback demonstrated a positive correlation between length and quality. Some reports indicate that feedback length does not contribute to quality improvement beyond a certain threshold [@Curtis2024-yo]. Considering that AI feedback length was sufficiently longer compared to supervisor feedback, our findings are consistent with these previous studies. Prior research has pointed out that busy physicians tend to provide short feedback, often lacking important elements such as specific examples and future action guidelines [@Lu2023-da; @Leclair2023-ul]. Our findings suggest that AI-generated feedback may be able to complement elements that tend to be missing in supervisors' brief feedback.

Regarding consistency in feedback quality, previous research has shown mixed results about whether AI or human feedback demonstrates greater consistency [@Mooney2022-hy; @Coughlin2022-qj; @Van-Ostaeyen2023-wo; @Ali2025-fd; @Lin2024-zt]. Our study found that AI feedback exhibited higher quality consistency compared to supervisor feedback. This consistency likely stems from AI's tendency to adhere closely to the evaluation rubric. Previous research has identified multiple factors that influence feedback quality variability, including feedback length [@Mooney2022-hy], the subject of feedback [@Coughlin2022-qj], and whether supervisors have received feedback training [@Renting2023-pk]. Our findings suggest that in busy clinical environments, AI could provide relatively stable feedback quality.

The distinction between text-anchored versus experience-based feedback represents a novel contribution of our study. Previous research has noted that AI feedback tends to provide comprehensive feedback closely tied to the target text [@Ali2025-fd; @Er2025-is], while human experts in specialized fields provide context-informed feedback which are perceived of higher quality [@Cicek2025-ru; @Zhou2025-fj]. Our study revealed that AI feedback was more likely to provide text-consistent feedback aligned with students' written clerkship logs, while supervisor feedback was more likely to draw on clinical experience, the whole context and feedback from a clinical expert's perspective. This suggests that the qualitative differences between AI and human expert feedback may become more pronounced in settings like clinical clerkships, where interpersonal relationships are intensive and professional expertise is more complex and specialized.

Regarding the ability to distinguish between AI and human feedback, previous studies have reported inconsistent findings [@Nazaretsky2024-sf; @Zhang2025-cg; @Rudian2025-nq]. In our study, all evaluators correctly identified the source of feedback with 100% accuracy. The differences we observed in text length, feedback structure, and clinical perspective in the busy clinical environment likely served as decisive factors for identification. These substantial differences suggest that AI feedback should not replace human feedback but rather complement it by leveraging their respective strengths.

### Implications of Findings

These findings have important implications for the integration of AI-generated feedback in clinical education. Our results suggest that AI-generated and supervisor-provided feedback each possess distinct strengths and limitations, and should be leveraged in a complementary manner rather than as replacements for one another. For instance, AI could provide structured, criterion-based feedback alongside supervisor feedback, allowing medical students to benefit from both perspectives. However, such direct provision of AI feedback requires careful consideration of potential risks, including student over-reliance on AI recommendations [@Khojasteh2025-vd] or conversely, dismissal of AI-generated insights [@Jayawardena2025-gj].

Various hybrid approaches merit exploration, including AI-drafted feedback refined by educators, role-based distribution where AI and supervisors focus on different aspects of student work, or AI enhancement of educator-authored feedback [@Banihashem2025-zo]. However, empirical research on these hybrid models remains limited, particularly in authentic clinical settings.

Future research should examine how learners respond to and utilize AI-generated feedback, and investigate the effectiveness of hybrid approaches that combine AI and supervisor feedback. Such studies will be essential for determining optimal implementation strategies for AI feedback systems in clinical clerkship environments, ensuring that technological capabilities enhance rather than disrupt the educational relationships and learning processes that are fundamental to clinical training.

### Limitations

Several limitations should be acknowledged in this study. First, as this research was conducted at a single institution, the generalizability of our findings to other institutions or cultural contexts needs to be confirmed. The specific characteristics of Nagoya University's clinical clerkship program and the Japanese medical education system may not be representative of other settings. Second, while our evaluators included both faculty and students, their individual backgrounds and experiences may have influenced their feedback evaluations. The relatively small number of evaluators (10 faculty and 10 students) may also limit the robustness of our findings. Third, this study employed a specific AI model (GPT-4o) for feedback generation, and results may differ with other AI models or future iterations of the technology. The prompt engineering process, while systematic, was tailored to our specific context and may not be optimal for other settings. Fourth, the evaluation rubric used to assess feedback quality, while validated in previous research, was adapted for our context and may have limited applicability to other educational settings or feedback purposes. Fifth, each dataset was evaluated by only one faculty member and one student, rather than by multiple independent raters. Inter-rater agreement was fair to moderate for supervisor feedback but poor for AI feedback, indicating that individual evaluator perspectives influenced ratings, particularly when assessing AI-generated output. Although the large number of datasets (N = 161) provides stability at the aggregate level, the precision of scores for individual datasets is limited. Finally, our study examined feedback on student logs but did not investigate how students actually utilize or respond to different types of feedback, which represents an important area for future investigation.

## Conclusions

This study revealed distinct strengths and limitations of AI-generated and supervisor-provided feedback on clinical clerkship portfolios. AI demonstrated the ability to consistently provide structured, rubric-adherent feedback, while struggling to offer clinically-grounded insights based on professional expertise. Conversely, supervisors provided contextually relevant feedback rooted in clinical experience, though their feedback tended to be brief and deviate from prescribed criteria in busy clinical environments. These findings suggest that AI-generated and supervisor feedback should be leveraged as complementary tools, with each addressing the limitations of the other to optimize student learning in clinical clerkship settings.

## Acknowledgements

We thank the following evaluators for their contribution to this study: Aya Shimotomai, Dai Iwata, Eishin Muramatsu, Hidekazu Kito, Hideki Takemi, Hiroaki Hakamata, Hirotake Machida, Kota Tokunaga, Mayuko Kitayama, Minoru Kishi, Naoki Yamada, Naomi Hino-Fukuyo, Nobuhiro Miyamae, Rikuto Kikunaga, Sou Suzuki, Takami Ishimoto, Takeshi Onoue, Tomokazu Kimura, Usukura Taiki, Yutaka Yamada, Yoshiki Tsumura, and Yuya Matsuura. We express our deep gratitude to all of them for their cooperation as evaluators in this study.

TK planned the study, developed the evaluation tools, created the research-related code, collected and analyzed the data, and wrote the manuscript. JD contributed to the study design, mainly focusing on the quantitative methods and evaluation of results, and improved the manuscript. NH contributed to the overall study design, organized the implementation structure for both quantitative and qualitative analyses, developed and translated the evaluation tools, and improved the manuscript. SR contributed to the study design, mainly focusing on the qualitative methods and evaluation of results, and improved the manuscript. SH contributed to the overall study design, coordinated the team, mainly focused on the qualitative methods and evaluation of results, and improved the manuscript.

GitHub Copilot (Ver. 0.35.2, AI models used: Claude Sonnet 4.5/Claude Opus4.5/GPT-4.1/GPT-5) and Claude Code (Claude Opus4.5) were used to assist in writing R code for quantitative analysis. The editor's predictive code‑generation feature was used for in-editor assistance. All generated code was reviewed, tested, and modified by TK, and reviewed by JD. For manuscript writing, the same AI agent was used to assist with translation from Japanese into English. After entering content in Japanese in the editor, we prompted the in-editor chat with "translate to english" and used the generated English text as the basis for additions and revisions to the manuscript. All generated text was checked and edited by TK, and reviewed and revised by all authors. For assistance with literature searches, Deep Research by ChatGPT (GPT-4o, GPT-5, GPT-5.1) was used. All selected articles were reviewed by TK, and results from hand searches were also compared and incorporated. 


This work was supported by JSPS KAKENHI Grant Number 25K06542.

## Conflicts of Interest
The authors have no conflicts of interest to declare.

## Multimedia Appendix 1

This file contains the feedback generation prompt for AI used in this study and its development process.

## Multimedia Appendix 2

This file contains the feedback evaluation rubric used in this study.

## Multimedia Appendix 3

This file contains the translation process into Japanese for the feedback evaluation rubric used in this study.

## References

::: {#refs}
:::
